### 2015-03-26 Projects/DelCo_2014/Report/Hose_Tests/DelCo_Hose_Tests_2014.tex
Delco_2014: Restructured and added east hose test descriptions to experimental procedure section

\subsubsection{East Structure Experiments}
\label{sec:East_Structure_Water_Flow_Procedure}
Five sets of water flow experiments (Tests 29-34) were conducted to observe the impact of different hose streams and application methods on the air flow in the East Structure. Water was flowed from the north side double doors into Room C during Tests 29-32 and from Room C into Room B for Tests 33 and 34. Tests 29 and 30 followed a similar procedure that differed in that Test 29 flowed water from a monitor in a straight stream pattern, while Test 30 flowed water from a monitor nozzle in a narrow fog pattern.

\subsubsection{West Structure Experiments}
\label{sec:West_Structure_Water_Flow_Procedure}

Four sets of water flow experiments (Tests 16-19) were conducted to observe the impact of using different hose streams and application patterns on the ventilation in the West Structure. Water was flowed from the double doors on the first floor for all experiments. The experiments varied based on flow path configurations and the type of nozzle used. Two flow path configurations were used. Both configurations contained the double doors on the first level in the opened position and the stairwell door and west side double door on the second level being opened and closed depending on the time in the experiment. The main difference between the two configurations was that the first level, south side door was in the opened position for Flow Path Configuration 1 and was in the closed position for Flow Path Configuration 2. Fig.~\ref{fig:flow_path_1} and Fig.~\ref{fig:flow_path_2} contain the floor plan schematics for Flow Path Configuration 1 and Flow Path Configuration 2, respectively.

\begin{figure}[!ht]
\includegraphics[trim=0cm 0cm 0.75cm 4.5cm, clip=true, width=6in]{../../Drawings/PDFs/Without_Instrumentation/West_Structure_Hose_Test_18_1st_Floor}
\\
\includegraphics[trim=0cm 0cm 0.75cm 5cm, clip=true, width=6in]{../../Drawings/PDFs/Without_Instrumentation/West_Structure_Hose_Test_18_2nd_Floor}
\caption[Flow path configuration used during West Structure water flow experiments]{West Structure first floor (top) and second floor (bottom) layouts for Test 18. Both double doors and the south side door were open on the first floor for the duration of the test. On the second floor, the stairwell door and north side, west double door were opened and closed during the experiments, while the north side, east double door and south side door were in the closed position throughout the entire test.}
\label{fig:flow_path_1}
\end{figure}

\begin{figure}[!ht]
\includegraphics[trim=0cm 0cm 0.75cm 4.5cm, clip=true, width=6in]{../../Drawings/PDFs/Without_Instrumentation/West_Structure_Hose_Test_19_1st_Floor}
\\
\includegraphics[trim=0cm 0cm 0.75cm 5cm, clip=true, width=6in]{../../Drawings/PDFs/Without_Instrumentation/West_Structure_Hose_Test_19_2nd_Floor}
\caption[West Structure first and second floor layouts for Test 19]{West Structure first floor (top) and second floor (bottom) layouts for Test 19. Both double doors were open and the south side door was closed on the first floor for the duration of the test. On the second floor, the stairwell door and north side, west double door were opened and closed during the experiments, while the north side, east double door and south side door were in the closed position throughout the entire test.}
\label{fig:flow_path_2}
\end{figure}

The four sets of water flow experiments conducted in the West Structure contained two different procedures for each flow path configuration. One of the procedures involved using a monitor nozzle to flow water at fixed positions in the first floor of the structure, and the other procedure used a handline equipped with a combination nozzle to flow water into the first floor of the structure in various application patterns.  The second procedure used a 1$\frac{3}{4}$" handline equipped with a combination nozzle to flow water in a straight stream, narrow fog stream, and wide fog stream pattern. Each stream was flowed in four different patterns: a fixed position, a sweeping pattern, a clockwise pattern, and a counter clockwise pattern.

\subsubsection{Monitor Nozzle Experimental Procedure}
\label{sec:Monitor_Procedure}
Two sets of the experiments, Tests 16 and 17, involved flowing water from a monitor nozzle in a straight stream, narrow fog stream, and wide fog stream pattern. Each stream was aimed at two different locations on the first floor interior ceiling: the "far target", which was located approximately X m (Xft) from the south interior wall, and the "near target" which was located approximately X m (Xft) from the interior wall of the double doors.

\subsubsection{Handline Experimental Procedure}
\label{sec:Handline_Procedure}
Two sets of experiments, Tests 18 and 19, involved flowing water in different stream patterns from a 1.75" handline equipped with a combination nozzle. Each hose stream was flowed in four different patterns: a fixed position, a sweeping pattern, a clockwise pattern, and a counter clockwise pattern.

Tests 18 and 19 followed identical procedures that involved flowing water from a handline using different hose stream and application pattern combination.  The handline combination nozzle was adjusted to produce three types of hose streams: a straight stream, a narrow fog stream, and a wide fog stream. Tests 18 and 19 involved three sets of experiments, one for each type of hose stream. For each set of experiments, four different application patterns were tested. First, water was applied while the hose was in a fixed position. Next, the hoseline was moved from side-to-side across the open room, creating a sweeping application pattern. Finally, the hoseline was rotated in both the clockwise and counterclockwise directions, creating clockwise and counterclockwise application patterns.

To begin each set of experiments, the combination nozzle was adjusted to produce the desired hose stream pattern. Once the nozzle was adjusted, water was applied while the hoseline was in the fixed position. After 60 seconds of water flow, the stairwell door was opened. 60 seconds after the stairwell door was opened, the north side, west double door on the second floor was opened, and water continued to flow for 60 more seconds. Then, the hoseline and two doors were closed, and the procedure was repeated for the sweeping, clockwise, and counterclockwise application patterns.

\begin{figure}[!ht]
\includegraphics[width=6in]{../../Figures/Test_18}
\caption[North Side of West Structure during Test 18]{North side of West Structure during Test 18. A straight stream pattern is being applied, and the flow path is fully established with the stairway door and the north side, west double door both opened.}
\label{fig:test_18_pic}
\end{figure}

>>>>

\subsubsection{Monitor Experiments}
\label{sec:Water_Flow_Monitor_Procedure}
A total of five sets of experiments were conducted using a monitor with a combination nozzle to flow water. Three of the tests (Tests 29, 30, and 33) occurred in the East Structure and two of the tests (Tests 16 and 17) occurred in the West Structure.

Tests 29 and 30 followed an identical procedure that involved flowing water from the north side double doors using a monitor with a combination nozzle. A straight stream pattern was used during Test 29, and a narrow fog stream pattern was used during Test 30. Each test began by flowing water with the nozzle aimed at the ceiling of Room C (marked in Fig.~\ref{fig:Test_29-32_setup}). After 30 seconds had elapsed, the south side door was opened for 30 seconds and then closed and the water flow was stopped. The monitor was adjusted so the nozzle was aimed at Door BC. Then, water flow began and after 30 seconds had elapsed, the south side door was opened for 30 seconds and then closed and the water flow was stopped. This process was repeated an additional time.

Test 33 varied from Tests 29 and 30 in multiple ways. First, for Test 33, the monitor was located inside Room C and aimed at the ceiling of Room B, as pictured in Fig.~\ref{fig:Test_33_34_setup}. Additionally, Test 33 began by flowing water in a straight stream pattern for 30 seconds, then in a narrow fog stream for 30 seconds, and finally in a wide fog stream for 30 seconds. Then, the south side door was opened, and each stream was applied for 30 seconds again.

Tests 16 and 17 followed an identical procedure that involved flowing water in a straight stream, narrow fog stream, and wide fog stream pattern from a monitor with a combination nozzle located at the south side, double doors on the first level of the West Structure. The difference between the tests was that Test 16 contained the flow path configuration presented in Fig.~\ref{fig:flow_path_1}, and Test 17 contained the flow path configuration presented in Fig.~\ref{fig:flow_path_2}. Tests 16 and 17 repeated an identical process three times, one time for each hose stream pattern. To begin the process, the nozzle was adjusted to produce the desired hose stream pattern. Once the nozzle was adjusted, water was applied at the ``far target", located on the ceiling approximately X m (Xft) from the south interior wall, for 60 seconds. After 60 seconds of water flow, the stairwell door was opened. 60 seconds after the stairwell door was opened, the north side, west double door on the second floor was opened, and water continued to flow for 60 more seconds. Then, water flow stopped, the two doors were closed, and the procedure was repeated with the monitor aimed at the ``near target", located approximately on the ceiling X m (Xft) from the interior wall of the double doors (Fig.~\ref{fig:Test_16_17}).

\subsubsection{Handline Experiments}
\label{sec:Water_Flow_Handline_Procedure}
A total of five sets of experiments were conducted using a 1.75" handline with a combination nozzle to flow water. Three of the tests (Tests 31, 32, and 34) occurred in the East Structure and two of the tests (Tests 18 and 19) occurred in the West Structure.

Tests 31 and 32 followed an identical procedure that involved flowing water from the north side double doors using a handline with a combination nozzle. A straight stream pattern was used during Test 31, and a narrow fog stream pattern was used during Test 32. Each test began by flowing water with the nozzle aimed at the ceiling of Room C (marked in Fig.~\ref{fig:Test_29-32_setup}) in the fixed position. After 30 seconds had elapsed, the nozzle was rotated in the clockwise direction and then returned to the fixed position of 30 seconds. Next, the nozzle was rotated in the counter-clockwise direction for 30 seconds, and then returned to the fixed position for 30 seconds. While the nozzle was in the fixed position, the south side door was opened and the application patterns were repeated. After the patterns were applied with the south side door opened, the door was closed, the handline was aimed at Door BC, and each pattern was applied again for thirty seconds while the south side door was opened and closed. This entire procedure was repeated an additional time.

Test 34 varied from Tests 31 and 32 in multiple ways. First, for Test 34, the handline was located inside Room C and aimed at the ceiling of Room B, as pictured in Fig.~\ref{fig:Test_33_34_setup}. Additionally, Test 34 began by flowing water in a straight stream at the ceiling in Room B for 30 seconds in a fixed position and then for 30 seconds in a clockwise application pattern. Then, the handline was aimed at Door AB, and again water was applied for 30 seconds in a fixed position and for 30 seconds in a clockwise pattern. These steps were repeated for narrow fog and wide fog streams. Additionally, the procedure was repeated for the three types of streams, except a counter clockwise pattern was applied.

Tests 18 and 19 followed an identical procedure that involved flowing water in a straight stream, narrow fog stream, and wide fog stream pattern from a handline with a combination nozzle located at the south side, double doors on the first level of the West Structure. The difference between the two tests was that Test 18 contained the flow path configuration presented in Fig.~\ref{fig:flow_path_1}, and Test 19 contained the flow path configuration presented in Fig.~\ref{fig:flow_path_2}. Tests 18 and 19 repeated an identical process three times, one time for each hose stream pattern. To begin the process, the nozzle was adjusted to produce the desired hose stream pattern. Once the nozzle was adjusted, water was applied while the hoseline was in the fixed position. After 60 seconds of water flow, the stairwell door was opened. 60 seconds after the stairwell door was opened, the north side, west double door on the second floor was opened, and water continued to flow for 60 more seconds. Then, water flow stopped, the two doors were closed, and the procedure was repeated for the sweeping, clockwise, and counterclockwise application patterns.

\begin{figure}[!ht]
\includegraphics[trim=0cm 0cm 0.75cm 4.5cm, clip=true, width=6in]{../../Drawings/PDFs/Without_Instrumentation/West_Structure_Hose_Test_18_1st_Floor}
\\
\includegraphics[trim=0cm 0cm 0.75cm 5cm, clip=true, width=6in]{../../Drawings/PDFs/Without_Instrumentation/West_Structure_Hose_Test_18_2nd_Floor}
\caption[West Structure first and second floor layouts for Tests 16 and 18]{West Structure first floor (top) and second floor (bottom) layouts for Tests 16 and 18. Both double doors and the south side door on the first floor were in the opened position for the duration of the test. On the second floor, the stairwell door and north side, west double door were opened and closed during the tests, while the north side, east double door and south side door were in the closed position throughout the entire test.}
\label{fig:flow_path_1}
\end{figure}
\FloatBarrier

\begin{figure}[!ht]
\includegraphics[trim=0cm 0cm 0.75cm 4.5cm, clip=true, width=6in]{../../Drawings/PDFs/Without_Instrumentation/West_Structure_Hose_Test_19_1st_Floor}
\\
\includegraphics[trim=0cm 0cm 0.75cm 5cm, clip=true, width=6in]{../../Drawings/PDFs/Without_Instrumentation/West_Structure_Hose_Test_19_2nd_Floor}
\caption[West Structure first and second floor layouts for Tests 17 and 19]{West Structure first floor (top) and second floor (bottom) layouts for Tests 17 and 19. Both double doors on the first floor were in the opened position and the south side door on the first floor was in the closed position for the duration of the test. On the second floor, the stairwell door and north side, west double door were opened and closed during the tests, while the north side, east double door and south side door were in the closed position throughout the entire test.}
\label{fig:flow_path_2}
\end{figure}
\FloatBarrier

\begin{figure}[!ht]
\includegraphics[width=6in]{../../Figures/Test_18}
\caption[North Side of West Structure during Test 18]{North side of West Structure during Test 18. A straight stream pattern is being applied, and the flow path is fully established with the stairway door and the north side, west double door both opened.}
\label{fig:test_18_pic}
\end{figure}
\FloatBarrier
